\bf A Concise Survey on Statistical Analysis in Bike Lane Research

### 2023-12-15 Manuscript/Manuscript.tex
changed formating for embedded euqations

A different approach that was used in the research into bike lanes was to use a zero-inflated Poisson regression model to estimate the change in cycle-motor vehicle collisions \cite{8Bhatia2016}. This model is used since the design is looking at collision rates pre to post instillation of bike lanes, and since the model allows for an over-abundance of zero counts in the data \cite{Giles2010}. The Poisson distribution's p.m.f is:
\[P(Y=y) = \exp{(-\lambda)\lambda^{y}}/y!\]

@@

Alongside this method, the cumulative curve method as used to extract traffic flow data from videos \cite{6Pu2017}. The basic model of the generalized linear model is:
\[Y_{nx1} = X_{nxp}\beta_{px1}+\epsilon_{nx1}\]
Where the matrix of observed values of dependent variables is  $Y_{nx1}$, $X_{nxp}$ is the matrix of observed explanatory variables, $\beta_{px1} =$ is the matrix of coefficients for explanatory variables, and $\epsilon_{nx1}$ is the error. Using this model is reported to help to understand how each factor contributed to the delay of cyclists on urban streets. In Figure ~\ref{fig:traffic}, the results are shown of results of the significance of multiple variables on vehicle delay, and it can be seen that with this method, bicycle and vehicle flow as well as the number of vehicle lanes, has a significant effect on vehicle delay. The results of flow vs. density are also shown in Figure ~\ref{fig:flow}, and reveals that the average bicycle speed decreases slightly as the density increases while  the flow is still increasing, and  when there is high density the variation of bicycle speed decreases a great deal. These results are also consistant across multople locations of urban streets. 
\begin{figure}[hbt!]
    \centering \includegraphics[width=1\textwidth]{BikeTrafficResults.png}
    \caption{Results table from Research on Bicycle Traffic from Pu et al.}
    \label{fig:traffic}
\end{figure}

>>>>

A different approach that was used in the research into bike lanes was to use a zero-inflated Poisson regression model to estimate the change in cycle-motor vehicle collisions \cite{8Bhatia2016}. This model is used since the design is looking at collision rates pre to post instillation of bike lanes, and since the model allows for an over-abundance of zero counts in the data \cite{Giles2010}. The model uses the Poisson distribution's p.m.f which is given my equation \ref{eq:2}:
\begin{equation} \label{eq:2}
P(Y=y) = \exp{(-\lambda)\lambda^{y}}/y!
\end{equation}

@@

Alongside this method, the cumulative curve method as used to extract traffic flow data from videos \cite{6Pu2017}. Equation \ref{eq:3} gives the basic model of the generalized linear model:
\begin{equation}\label{eq:3}
Y_{nx1} = X_{nxp}\beta_{px1}+\epsilon_{nx1}
\end{equation}
Where the matrix of observed values of dependent variables is  $Y_{nx1}$, $X_{nxp}$ is the matrix of observed explanatory variables, $\beta_{px1} =$ is the matrix of coefficients for explanatory variables, and $\epsilon_{nx1}$ is the error. Using this model is reported to help to understand how each factor contributed to the delay of cyclists on urban streets. In Figure ~\ref{fig:traffic}, the results are shown of results of the significance of multiple variables on vehicle delay, and it can be seen that with this method, bicycle and vehicle flow as well as the number of vehicle lanes, has a significant effect on vehicle delay. The results of flow vs. density are also shown in Figure ~\ref{fig:flow}, and reveals that the average bicycle speed decreases slightly as the density increases while  the flow is still increasing, and  when there is high density the variation of bicycle speed decreases a great deal. These results are also consistant across multople locations of urban streets. 
\begin{figure}[hbt!]
    \centering \includegraphics[width=1\textwidth]{BikeTrafficResults.png}
    \caption{Results table from Research on Bicycle Traffic from Pu et al.}
    \label{fig:traffic}
\end{figure}
